---
title: "Exercise 7"
format: docx
---

In RStudio, do the following in *two* documents.

1. In a Quarto document with `format: docx`, wrangle the customer data to include the total amount spent in-store for each customer. Write this data as a CSV file *in the Exercises folder*.
2. In an R Markdown document, modify the dashboard from class by importing the new data, adding a second input function to the sidebar to select from `college_degree`, modifying the plot to filter on both input functions, replacing age with total amount spent in-store in the plot, and modifying the call-out boxes to filter on both input functions.
3. Knit the R Markdown document and publish it on shinyapps.io. Include the link at the end of the Quarto document (add a link with `[text](URL)`), rendered as a Word document, and upload to Canvas.

**Five points total, one point each for:**

- **Wrangling to get the new crm_data.**
- **Adding the `college_degree` input to the dashboard.**
- **Modifying the plot and value boxes in the dashboard.**
- **Publishing to shinyapps.io.**
- **Submitting a rendered Word document with the link included.**

## Import and Wrangle Data

We first need to get the `store_revenue` data. I've already connected to the database and written it locally, but here are the steps I took.

```{r}
# Load packages.
library(tidyverse)
library(dplyr)
library(DBI)
```

```{r}
#| eval: false

# Connect to the database.
con <- dbConnect(
  RPostgreSQL::PostgreSQL(),
  dbname = "analyticsdb",
  host = "analyticsdb.ccutuqssh92k.us-west-2.rds.amazonaws.com",
  port = 55432,
  user = "quantmktg",
  password = rstudioapi::askForPassword("Database password")
)

# Import the data.
store_revenue <- tbl(con, "store_revenue") |>
  collect()

# Disconnect from the database.
dbDisconnect(con)

# Write as a CSV.
write_csv("store_revenue.csv")
```

Now to import the data that I have locally.

```{r}
# Import the data.
customer_data <- read_csv("customer_data.csv")
store_revenue <- read_csv("store_revenue.csv")
```

Now we can tidy the data to calculate the amount spent in-store for each customer.

```{r}
# Summarize the amount spent overall by each customer.
total_spent <- store_revenue |> 
  pivot_longer(
    -customer_id,
    names_to = "month_year",
    values_to = "amount_spent"
  ) |> 
  group_by(customer_id) |> 
  summarize(total_spent = sum(amount_spent))

# Join the new total_spent column onto the rest of customer_data.
crm_data <- customer_data |> 
  left_join(total_spent, join_by(customer_id))

# Write the new crm_data as a CSV in Exercises.
write_csv(crm_data, "crm_data.csv")
```

## Dashboard

You can see my modified Patagonia CRM Dashboard [here](https://marcdotson.shinyapps.io/exercise_08/).

